Constraints on tensor and scalar couplings from $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-08-03 tensor/draft/draft-tensor-op.tex
[draft-tensor-op.tex] added Danny's comments to draft

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
  depends on two parameters, the lepton forward-backward asymmetry, $A_{\rm
    FB}^\ell$, and the flat term, $F_H^\ell$. Both are strongly suppressed in
  the standard model and constitute sensitive probes of tensor and scalar
  contributions. We use the latest experimental results for $\ell = \mu$ in
  combination with $B_s\to \bar\mu\mu$ to derive the strongest model-independent
  bounds on tensor and scalar effective couplings to date. The measurement of
  $F_H^\mu$ \christoph{provides complementary constraints} to that of the branching ratio of $B_s\to
  \bar\mu\mu$ and allows us---for the first time---to constrain all
  complex-valued (pseudo-)scalar couplings and their chirality-flipped
  counterparts in one fit. Based on Bayesian fits of various scenarios, we find
  that our bounds even become tighter when vector couplings are allowed to
  deviate from the standard model and that specific combinations of angular
  observables in $B \to K^*$ are still allowed to be up to two orders of
  magnitude larger than in the standard model, which would place them in the
  region of LHCb's sensitivity.
\end{abstract}

@@

Both observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
factors for vector and dipole couplings present in the SM, thereby enhancing
their sensitivity to tensor and scalar couplings \cite{Bobeth:2007dw,
  Bobeth:2012vn}. A similar enhancement of scalar couplings compared to
helicity-suppressed vector couplings of the SM is well-known from $B_s\to
\bar\mu\mu$. Unfortunately the limited data set of $B\to K^*(\to K\pi)
\bar\ell\ell$ from LHCb \cite{Aaij:2013qta} \christoph{did not yet} allow to perform a full
angular analysis without the assumption of vanishing scalar and tensor couplings
in this decay mode. In the future with more data or special-purpose analysis
techniques like the method of moments~\cite{beaujean:2015mom}, certain angular
observables in $B\to K^* \bar\ell\ell$ will provide additional constraints on
such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz} and the
linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
\cite{Matias:2012xw, Bobeth:2012vn} as well as the experimental test of the
relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn} at low
hadronic recoil.

@@

In the framework of the $|\Delta B| = |\Delta S| = 1$ effective theory
\begin{equation}
  \label{eq:Heff}
\begin{aligned}
  {\cal L}_{\rm eff}  =
   \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, & V_{tb}^{} V_{ts}^\ast
      \, \Big[ \christoph{C_7(\mu_b) \Op_7 + C_{7'}(\mu_b) \Op_{7'}}
 \\ & +
       \sum_{\ell = e,\, \mu,\, \tau} \sum_i  \wilson[\ell]{i}(\mu_b)  \Op_i \Big] + \text{h.c.}
   \christoph{\,,}
\end{aligned}
\end{equation}
the most general dimension-six flavor-changing operators $\Op_i$ mediating $b\to
s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their chiral
structure. There are dipole ($i = 7,7'$) and vector ($i = 9,9',10,10'$) operators
\begin{equation}
  \label{eq:SM:ops}
\begin{aligned}
  \Op_{7(7')} &
  = \frac{m_b}{e}\!\[\bar{s} \sigma^{\mu\nu} P_{R(L)} b\] F_{\mu\nu}\,,
\\
  \Op_{9(9')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \ell\]\,,
\\[0.1cm]
  \Op_{10(10')} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
further scalar ($i = S,S',P,P'$) operators
\begin{equation}
  \label{eq:scalar:ops}
\begin{aligned}
  \Op_{S(S')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \ell\]\,,
\\[0.1cm]
  \Op_{P(P')} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
and tensor ($i = T,T5$) operators
\begin{equation}
  \label{eq:tensor:ops}
\begin{aligned}
  \Op_{T} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \ell\]\,,
\\[0.1cm]
  \Op_{T5} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
where the notation $\Op_{T5} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
\[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
also used frequently in the literature. The respective short-distance couplings,
the Wilson coefficients $\wilson[(\ell)]{i}(\mu_b)$ are evaluated at a scale of
the order of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM
predictions in the presence of new physics.

The SM values $\wilson[(\ell)]{7,9,10}$ are obtained at next-to-next-to leading order
(NNLO) \cite{Bobeth:2003at, Huber:2005ig} and depend on the fundamental parameters
of the top-quark and $W$-boson masses, as well as on the sine of the weak mixing angle.
Moreover, they are universal for the three lepton flavors $\ell = e,\, \mu,\, \tau$.
All other Wilson coefficients are numerically suppressed or zero:
$\wilson[SM]{7'} = m_s/m_b\, \wilson[SM]{7}$, $\wilson[\ell, SM]{S,S',P,P'} \sim
{\cal O}(m_b^2/m_W^2)$, and $\wilson[\ell, SM]{9',10',T,T5} = 0$.
%Beyond the SM,
%lepton-flavor non-universal effects are possible in principle and have been
%discussed for example recently \cite{Alonso:2014csa, Hiller:2014yaa, Ghosh:2014awa,
%Biswas:2014gga, Hurth:2014vma, Glashow:2014iga, Altmannshofer:2014rta, Hiller:2014abc} in
%connection with the measurement of $R_K = {\cal B}_\mu/{\cal B}_e$ in
%$q^2 \in [1, 6]$ GeV$^2$ \cite{Aaij:2014ora}, which deviates by $2.6\sigma$
%from the SM prediction $R_K^{\rm SM} = 1.00$ \cite{Bobeth:2007dw, Bouchard:2013mia}.
The Wilson coefficients of the four-quark current-current and QCD-penguin
operators as well as of the chromomagnetic dipole operators are set to their
NNLO SM values at $\mu_b = 4.2 \, \mbox{GeV}$ \cite{Bobeth:2003at, Huber:2005ig}.

\christoph{For the rest of this article we will suppress the lepton-flavor index
on the Wilson coefficients: $\wilson[\ell]{i} \to \wilson[]{i}$. In \refsec{sec:results}
we exploit data with $\ell =\mu$ only, hence all derived constraints apply in
principle only to the muonic case, but can be carried over to other lepton
species $\ell = e,\, \tau$ in cases of NP models that do not violate lepton
flavor. In general the Wilson coefficients are decomposed into SM and NP
contributions $\wilson[]{i} = \wilson[SM]{i} + \wilson[NP]{i}$, but often we
will use $\wilson[]{i}$ for Wilson coefficients with zero (or suppressed) SM 
contributions synonymously for $\wilson[NP]{i}$. }

@@

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with \christoph{$\mbox{dim} \geq 8$}. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2} 
    \christoph{\bigg/ \Gamma_\ell} \,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests. 
The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed \christoph{by small 
lepton masses for the considered kinematical region $1 \leq q^2 \leq 22$ GeV$^2$}
\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.  
Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED 
corrections, which will modify the simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
available for this source of SM background\footnote{The leading QED corrections
  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} \todo{(update ref. with published)} might provide an estimate of
  corresponding effects in $B\to K \bar\ell\ell$.}. \todo{David's comment?!}

@@

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \begin{center}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
    % \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \end{center}
  \caption{ The sensitivity to the tensor coupling $\mbox{Re}(\wilson{T})$ of
    \christoph{$F_H^\mu$} (first row) and \christoph{${\cal B}_\mu$} (second row) 
    in $B^+ \to K^+ \bar\mu\mu$
    \christoph{as well as} \christoph{${\cal B}_\mu$} (third row), $(J_{1c} + J_{2c})$ 
    (fourth row), and $(J_{1s}-3 J_{2s})$ (fifth row) in $B^0 \to K^{*0} \bar\mu\mu$ 
    integrated over low- and high-$q^2$ bins. In the last two rows, the observables 
    are rescaled by the
    lifetime of the $B$ meson for easier comparison with the branching
    ratios. The bands represent the theory uncertainties at 68\% and 95\%
    probability of the prior predictive distribution.  For comparison, two sets
    of bands are shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
    $\wilson[NP]{9} = -1.1$ (red), and an additional band of the latest 68\%
    confidence interval reported by LHCb (grey) if a measurement is
    available. \checked{} }
  \label{fig:FHvsCT}
\end{figure*}

@@

Only tensor contributions enter
\begin{align}
  (J_{1s} - 3\, J_{2s}) & \propto
  \left(\ldots |\wilson{T}|^2 + \ldots |\wilson{T5}|^2 \right) \,,
\end{align}
where the dots indicate different kinematic and form-factor dependencies.  But
tensor \emph{and} scalar contributions enter
\begin{equation}
\begin{aligned}
  (J_{1c} + J_{2c}) & \propto
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2 \right)
\\
  & + \ldots \left(|\wilson{S} - \wilson{S'}|^2 + |\wilson{P} - \wilson{P'}|^2 \right) \,,
\end{aligned}
\end{equation}
which is similar to the dependence of $F_H^\ell$ in $B\to K
\bar\ell\ell$
\begin{equation}
  \label{eq:FH-dependence}
\begin{aligned}
  F_H^\ell  \propto & \Big[
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2\right)
\\
  & + \ldots \left(|\wilson{S} + \wilson{S'}|^2 + |\wilson{P} + \wilson{P'}|^2 \right)
  \Big]
  \Big/ \Gamma_\ell \,.
\end{aligned}
\end{equation}
Concerning $F_H^\ell$, the involved kinematic factors---see \cite{Bobeth:2007dw,
  Bobeth:2012vn}---are such that tensor and scalar couplings contribute only
constructively/cumulatively, apart from cancellations among $\wilson{S(P)}$ and
$\wilson{S'(P')}$.  Interference terms in the numerator of $F_H^\ell$ of the
form $(\wilson{T} \times \wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times
\wilson{10,10'})$ are suppressed by $m_\ell/\sqrt{q^2}$. They can only become
relevant in case $\wilson{T} \ll \wilson{7,7',9,9'}$ or $\wilson{P,P'}
\ll\wilson{10,10'}$.

@@

In the following we consider a model-independent scenario \christoph{consisting
of the SM augmented} by dimension six operators that respect the SM gauge group and are
composed of SM fields only. Such a scenario becomes more and more viable for two
reasons. The first is the discovery of a scalar resonance at the LHC in
agreement with all requirements of the Higgs particle in the SM. The second are
the steadily rising lower bounds on the mass of new particles reported by ATLAS
and CMS in various more or less specific models.

@@

We rescale the observables by the $B^0$-meson life time $\tau_{B^0} =
1.519$~ps~\cite{Agashe:2014kda} to be able to judge if experiments can measure
them in the near future.  At low $q^2$ the posterior predictive ranges are
${\cal O}(10^{-9})$ for $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$, getting
suppressed down to ${\cal O}(10^{-10})$ at high $q^2$ due to the
$m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical magnitude
of vector couplings, note that for example the branching ratio of $B\to
K^*\bar\ell\ell$
\begin{align}
  \BR &
  = \frac{\tau_{B^0}}{3} \big[
    2\, (3 J_{1s} - J_{2s}) + (3 J_{1c} -  J_{2c})
  \big]
\end{align}
is approximately equal to $2 \cdot 10^{-7}$ in the SM for both the
\christoph{$q^2 \in [1.1,\, 6]$} and $[15,\, 19]$ GeV$^2$ bins.

The angular observable $J_{6c}$ is strictly zero in the absence of tensor and
scalar couplings. Nonzero contributions can be generated in the SM by QED
corrections or potentially from higher-dimensional ($d \geq 8$) $|\Delta B| =
|\Delta S| = 1$ operators, leading to parametric suppression by $\alpha_e/(4
\pi)$ or $(m_b/m_W)^2$. These factors should be compared to the potential
suppression present for tensor and scalar contributions in particular NP models
in order to gauge their relevance. Our model-independent fits are still in a
regime where such considerations are insignificant since current experimental
measurements, in combination with theory uncertainties, do not yet impose too
stringent constraints on tensor and scalar couplings.

@@

In a Bayesian analysis of the complex-valued couplings of the effective theory,
we find that the measurement of $F_H^\mu$, especially at high-$q^2$,
\begin{enumerate}
  \item imposes by itself \christoph{constraints} on tensor couplings $|\wilson{T,\,T5}|$ such
  that the upper bound of the smallest 68\% (95\%) credibility interval is
  $0.43\, (0.57)$, superseding previous bounds.  In combination with current
  data from $B\to K^* \bar\mu\mu$ and lattice \christoph{predictions of} $B\to K^*$ form factors, the
  bounds are lowered to 0.33 (0.43), even in the presence of nonstandard
  contributions in vector couplings.
  \item for the first time allows to bound all four scalar couplings
  \christoph{$\wilson{i = S,S',P,P'}$} due to it's complementarity to
  $\overline{\cal B}(B_s \to \bar\mu\mu)$. Even when taking into account
  destructive interference with vector couplings, $|\wilson{i} + \wilson{i'}| <
  0.3\, (0.6)$ and $|\wilson{i} - \wilson{i'}| < 0.1\, (0.2)$ for $i = S,P$ with
  at least 68\% (95\%) probability. Currently, the bounds from $F_H^\mu$ are
  weaker than those from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by about a
  factor of four. Future measurements of $F_H^\mu$ at LHCb and Belle II will
  further tighten the bounds.

@@

%\todo{this is just filler text to avoid ``pdfendlink ended up in different
%  nesting level than pdfstartlink’'' because entry \cite{Horgan:2013pva} is broken across two pages
%}

>>>>

\begin{abstract}
  The angular distribution of $B\to K\bar\ell\ell$ ($\ell = e,\,\mu,\,\tau$)
  depends on two parameters, the lepton forward-backward asymmetry, $A_{\rm
    FB}^\ell$, and the flat term, $F_H^\ell$. Both are strongly suppressed in
  the standard model and constitute sensitive probes of tensor and scalar
  contributions. We use the latest experimental results for $\ell = \mu$ in
  combination with \christoph{branching ratio of} $B_s\to \bar\mu\mu$ to derive the strongest model-independent
  bounds on tensor and scalar effective couplings to date. The measurement of
  $F_H^\mu$ \christoph{provides complementary constraints} to that of the branching ratio of $B_s\to
  \bar\mu\mu$ and allows us---for the first time---to constrain all
  complex-valued (pseudo-)scalar couplings and their chirality-flipped
  counterparts in one fit. Based on Bayesian fits of various scenarios, we find
  that our bounds even become tighter when vector couplings are allowed to
  deviate from the standard model and that specific combinations of angular
  observables in $B \to K^*$ are still allowed to be up to two orders of
  magnitude larger than in the standard model, which would place them in the
  region of LHCb's sensitivity.
\end{abstract}

@@

Both \christoph{angular} observables, $F_H^\ell$ and $A_{\rm FB}^\ell$, exhibit strong suppression
factors for vector and dipole couplings present in the SM, thereby enhancing
their sensitivity to tensor and scalar couplings \cite{Bobeth:2007dw,
  Bobeth:2012vn}. A similar enhancement of scalar couplings compared to
helicity-suppressed vector couplings of the SM is well-known from $B_s\to
\bar\mu\mu$. Unfortunately the limited data set of $B\to K^*(\to K\pi)
\bar\ell\ell$ from LHCb \cite{Aaij:2013qta} \christoph{did not yet} allow to perform a full
angular analysis without the assumption of vanishing scalar and tensor couplings
in this decay mode. In the future with more data or special-purpose analysis
techniques like the method of moments~\cite{beaujean:2015mom}, certain angular
observables in $B\to K^* \bar\ell\ell$ will provide additional constraints on
such couplings, as for example $J_{6c}$ \cite{Altmannshofer:2008dz} and the
linear combinations $(J_{1s} - 3 J_{2s})$ and $(J_{1c} + J_{2c})$
\cite{Matias:2012xw, Bobeth:2012vn} as well as the experimental test of the
relations $H_T^{(2)} = H_T^{(3)}$ and $J_7 = 0$~\cite{Bobeth:2012vn} at low
hadronic recoil.

@@

In the framework of the $|\Delta B| = |\Delta S| = 1$ effective theory
\begin{equation}
  \label{eq:Heff}
\begin{aligned}
  {\cal L}_{\rm eff}  =
   \frac{4 G_F}{\sqrt{2}} \,\frac{\alE}{4 \pi}\, & V_{tb}^{} V_{ts}^\ast
      \, \Big[ \christoph{C_7(\mu_b) \Op_7 + C_{7'}(\mu_b) \Op_{7'}}
 \\ & +
       \sum_{\ell = e,\, \mu,\, \tau} \sum_i  \wilson[\ell]{i}(\mu_b)
       \christoph{\Op_i^\ell} \Big] + \text{h.c.}
   \christoph{\,,}
\end{aligned}
\end{equation}
the most general dimension-six flavor-changing operators \christoph{$\Op_i^{(\ell)}$} mediating $b\to
s \gamma$ and $b\to s \bar\ell\ell$ are classified according to their chiral
structure. There are dipole ($i = 7,7'$) and vector ($i = 9,9',10,10'$) operators
\begin{equation}
  \label{eq:SM:ops}
\begin{aligned}
  \Op_{7(7')} &
  = \frac{m_b}{e}\!\[\bar{s} \sigma^{\mu\nu} P_{R(L)} b\] F_{\mu\nu}\,,
\\
  \christoph{\Op_{9(9')}^\ell} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \ell\]\,,
\\[0.1cm]
  \christoph{\Op_{10(10')}^\ell} &
  = \[\bar{s} \gamma_\mu P_{L(R)} b\]\!\[\bar{\ell} \gamma^\mu \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
further scalar ($i = S,S',P,P'$) operators
\begin{equation}
  \label{eq:scalar:ops}
\begin{aligned}
  \christoph{\Op_{S(S')}^\ell} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \ell\]\,,
\\[0.1cm]
  \christoph{\Op_{P(P')}^\ell} &
  = \[\bar{s} P_{R(L)} b\]\!\[\bar{\ell} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
and tensor ($i = T,T5$) operators
\begin{equation}
  \label{eq:tensor:ops}
\begin{aligned}
  \christoph{\Op_{T}^\ell} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \ell\]\,,
\\[0.1cm]
  \christoph{\Op_{T5}^\ell} &
  = \[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma^{\mu\nu} \gamma_5 \ell\]\,,
\end{aligned}
\end{equation}
where the notation $\christoph{\Op_{T5}^\ell} = i/2\, \varepsilon^{\mu\nu\alpha\beta}
\[\bar{s} \sigma_{\mu\nu} b\]\!\[\bar{\ell} \sigma_{\alpha\beta} \ell\]$ is
also used frequently in the literature. The respective short-distance couplings,
the Wilson coefficients $\wilson[(\ell)]{i}(\mu_b)$ are evaluated at a scale of
the order of the $b$-quark mass $\mu_b \sim m_b$ and can be modified from SM
predictions in the presence of new physics.

The SM values $\wilson[(\ell)]{7,9,10}$ are obtained at next-to-next-to leading order
(NNLO) \cite{Bobeth:2003at, Huber:2005ig} and depend on the fundamental parameters
of the top-quark and $W$-boson masses, as well as on the sine of the weak mixing angle.
Moreover, they are universal for the three lepton flavors $\ell = e,\, \mu,\, \tau$.
All other Wilson coefficients are numerically suppressed or zero:
$\wilson[SM]{7'} = m_s/m_b\, \wilson[SM]{7}$, $\wilson[\ell, SM]{S,S',P,P'} \sim
\christoph{m_b m_\ell/m_W^2}$, and $\wilson[\ell, SM]{9',10',T,T5} = 0$.
%Beyond the SM,
%lepton-flavor non-universal effects are possible in principle and have been
%discussed for example recently \cite{Alonso:2014csa, Hiller:2014yaa, Ghosh:2014awa,
%Biswas:2014gga, Hurth:2014vma, Glashow:2014iga, Altmannshofer:2014rta, Hiller:2014abc} in
%connection with the measurement of $R_K = {\cal B}_\mu/{\cal B}_e$ in
%$q^2 \in [1, 6]$ GeV$^2$ \cite{Aaij:2014ora}, which deviates by $2.6\sigma$
%from the SM prediction $R_K^{\rm SM} = 1.00$ \cite{Bobeth:2007dw, Bouchard:2013mia}.
The Wilson coefficients of the four-quark current-current and QCD-penguin
operators as well as of the chromomagnetic dipole operators are set to their
NNLO SM values at $\mu_b = 4.2 \, \mbox{GeV}$ \cite{Bobeth:2003at, Huber:2005ig}.

\christoph{For the rest of this article we will suppress the lepton-flavor index
on the Wilson coefficients: $\wilson[\ell]{i} \to \wilson[]{i}$ and 
operators $\Op_i^\ell \to \Op_i$. In \refsec{sec:results}
we exploit data with $\ell =\mu$ only, hence all derived constraints apply in
principle only to the muonic case, but can be carried over to other lepton
species $\ell = e,\, \tau$ in cases of NP models that do not violate lepton
flavor. In general the Wilson coefficients are decomposed into SM and NP
contributions $\wilson[]{i} = \wilson[SM]{i} + \wilson[NP]{i}$, but often we
will use $\wilson[]{i}$ for Wilson coefficients with zero (or suppressed) SM 
contributions synonymously for $\wilson[NP]{i}$. }

@@

The full dependence of $F_H^\ell$ and $A_{\rm FB}^\ell$ on tensor and scalar
couplings has been presented in \cite{Bobeth:2007dw, Bobeth:2012vn}, adopting
the effective theory \refeq{eq:Heff}, i.e. neglecting higher dimensional operators
with \christoph{$\mbox{dim} \geq 8$}. These results imply that for SM values of the effective
couplings
\begin{align}
  F_H^\ell(q^2) \big|_{\rm SM} & \propto \frac{m_\ell^2}{q^2} 
    \christoph{\bigg/ \Gamma_\ell} \,, &
  A_{\rm FB}^\ell \big|_{\rm SM} & = 0 \,.
\end{align}
Hence, for $\ell = e,\, \mu$ both observables are quasi-null tests. 
The flat term $F_H^\ell(q^2)|_{\rm SM}$ is strongly suppressed \christoph{by small 
lepton masses for the considered kinematical region $1 \leq q^2 \leq 22$ GeV$^2$}
\cite{Bobeth:2007dw, Bobeth:2011nj, Bouchard:2013eph}.  
Nonzero values of $A_{\rm FB}^\ell|_{\rm SM}$ can be induced by higher order QED 
corrections, which will modify the simple $\cos\theta_\ell$ dependence of the angular
distribution~\refeq{eq:ang-distr}, however, currently there is no solid estimate
available for this source of SM background\footnote{The leading QED corrections
  to $B\to X_s\bar\ell\ell$ \cite{Huber:2015sra} might provide an estimate of
  corresponding effects in $B\to K \bar\ell\ell$.}. \todo{David's comment?!}

@@

\begin{figure*}
  \setlength{\relwidth}{0.33\textwidth}
  \begin{center}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR1to6}
    % \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR14to16}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_BR16to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1c_plus_J_2c15to19}
    \\
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s1to6}
    \includegraphics[width=\relwidth]{plots/pdf/ct_Kstar_J_1s_minus_3J_2s15to19}
  \end{center}
  \caption{ The sensitivity of to the tensor coupling $\mbox{Re}(\wilson{T})$
    of\christoph{: $F_H^\mu$} (first row) and \christoph{${\cal B}_\mu$} (second row) 
    in $B^+ \to K^+ \bar\mu\mu$
    \christoph{as well as} \christoph{${\cal B}_\mu$} (third row), $(J_{1c} + J_{2c})$ 
    (fourth row), and $(J_{1s}-3 J_{2s})$ (fifth row) in $B^0 \to K^{*0} \bar\mu\mu$ 
    integrated over low- and high-$q^2$ bins. In the last two rows, the observables 
    are rescaled by the
    lifetime of the $B$ meson for easier comparison with the branching
    ratios. The bands represent the theory uncertainties at 68\% and 95\%
    probability of the prior predictive distribution.  For comparison, two sets
    of bands are shown for the SM, $\wilson[NP]{9} = 0$ (blue), and
    $\wilson[NP]{9} = -1.1$ (red), and an additional band of the latest 68\%
    confidence interval reported by LHCb (grey) if a measurement is
    available. }
  \label{fig:FHvsCT}
\end{figure*}

@@

Only tensor contributions enter
\begin{align}
  (J_{1s} - 3\, J_{2s}) & \propto
  \left(\ldots |\wilson{T}|^2 + \ldots |\wilson{T5}|^2 \right) \,,
\end{align}
where the dots indicate different kinematic and form-factor dependencies.  But
tensor \emph{and} scalar contributions enter
\begin{equation}
\begin{aligned}
  (J_{1c} + J_{2c}) & \propto
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2 \right)
\\
  & + \ldots \left(|\wilson{S} - \wilson{S'}|^2 + |\wilson{P} - \wilson{P'}|^2 \right) \,,
\end{aligned}
\end{equation}
which is similar to the dependence of $F_H^\ell$ in $B\to K
\bar\ell\ell$
\begin{equation}
  \label{eq:FH-dependence}
\begin{aligned}
  F_H^\ell  \propto & \Big[
      \ldots \left(|\wilson{T}|^2 + |\wilson{T5}|^2\right)
\\
  & + \ldots \left(|\wilson{S} + \wilson{S'}|^2 + |\wilson{P} + \wilson{P'}|^2 \right)
  \Big]
  \Big/ \Gamma_\ell \,.
\end{aligned}
\end{equation}
Concerning $F_H^\ell$, the involved kinematic factors---see \cite{Bobeth:2007dw,
  Bobeth:2012vn}---are such that tensor and scalar couplings contribute only
constructively/cumulatively, apart from cancellations among $\wilson{S(P)}$ and
$\wilson{S'(P')}$.  Interference terms in the numerator of $F_H^\ell$ of the
form $(\wilson{T} \times \wilson{7,7',9,9'})$ and $(\wilson{P,P'} \times
\wilson{10,10'})$ are suppressed by $m_\ell/\sqrt{q^2}$. \christoph{They become numerically
relevant in cases $\wilson{T} \ll \wilson{7,7',9,9'}$ or $\wilson{P,P'}
\ll\wilson{10,10'}$, where the smallness of Wilson coefficient is of the
same level as the suppression factor $m_\ell/\sqrt{q^2}$ of the large vectorial
SM Wilson coefficients $\wilson[SM]{9,10}$, which implies however no large
enhancement of $F_H^\ell$ over the SM prediction.}

@@

In the following we consider a \christoph{scenario consisting
of the SM augmented} by dimension six operators that respect the SM gauge group and are
composed of SM fields only. Such a scenario becomes more and more viable for two
reasons. The first is the discovery of a scalar resonance at the LHC in
agreement with all requirements of the Higgs particle in the SM. The second are
the steadily rising lower bounds on the mass of new particles reported by ATLAS
and CMS in various more or less specific models.

@@

\todo{Fred should clarify with Danny on their paper.}
We rescale the observables by the $B^0$-meson life time $\tau_{B^0} =
1.519$~ps~\cite{Agashe:2014kda} to be able to judge if experiments can measure
them in the near future.  At low $q^2$ the posterior predictive ranges are
${\cal O}(10^{-9})$ for $(J_{1s} - 3\, J_{2s})$ and $(J_{1c} + J_{2c})$, getting
suppressed down to ${\cal O}(10^{-10})$ at high $q^2$ due to the
$m_\ell/\sqrt{q^2}$ dependence. In order to compare it to the typical magnitude
of vector couplings, note that for example the branching ratio of $B\to
K^*\bar\ell\ell$
\begin{align}
  \christoph{\BR} &
  = \frac{\tau_{B^0}}{3} \big[
    2\, (3 J_{1s} - J_{2s}) + (3 J_{1c} -  J_{2c})
  \big]
\end{align}
is approximately equal to $2 \cdot 10^{-7}$ in the SM for both the
\christoph{$q^2 \in [1.1,\, 6]$} and $[15,\, 19]$ GeV$^2$ bins.

The angular observable $J_{6c}$ is strictly zero in the absence of tensor and
scalar couplings. Nonzero contributions can be generated in the SM by QED
corrections or potentially from higher-dimensional ($d \geq 8$) $|\Delta B| =
|\Delta S| = 1$ operators, leading to parametric suppression by $\alpha_e/(4
\pi)$ or \christoph{$m_b m_\ell/m_W^2$}. These factors should be compared to the potential
suppression present for tensor and scalar contributions in particular NP models
in order to gauge their relevance. Our model-independent fits are still in a
regime where such considerations are insignificant since current experimental
measurements, in combination with theory uncertainties, do not yet impose 
\christoph{sufficiently}
stringent constraints on tensor and scalar couplings.

@@

In a Bayesian analysis of the complex-valued couplings of the effective theory,
we find that the measurement of $F_H^\mu$, especially at high-$q^2$,
\begin{enumerate}
  \item imposes by itself \christoph{constraints} on tensor couplings $|\wilson{T,\,T5}|$ such
  that the upper bound of the smallest 68\% (95\%) credibility interval is
  $0.43\, (0.57)$, superseding previous bounds.  In combination with current
  data from $B\to K^* \bar\mu\mu$ and lattice \christoph{predictions of} $B\to K^*$ form factors, the
  bounds are lowered to 0.33 (0.43), even in the presence of nonstandard
  contributions in vector couplings.
  \item for the first time allows to \christoph{simultaneously} bound all four scalar couplings
  \christoph{$\wilson{i = S,S',P,P'}$} due to it's complementarity to
  $\overline{\cal B}(B_s \to \bar\mu\mu)$. Even when taking into account
  destructive interference with vector couplings, $|\wilson{i} + \wilson{i'}| <
  0.3\, (0.6)$ and $|\wilson{i} - \wilson{i'}| < 0.1\, (0.2)$ for $i = S,P$ with
  at least 68\% (95\%) probability. Currently, the bounds from $F_H^\mu$ are
  weaker than those from $\overline{\cal B}(B_s \to \bar\mu\mu)$ by about a
  factor of four. Future measurements of $F_H^\mu$ at LHCb and Belle II will
  further tighten the bounds.

@@
